### 2025-02-14 paper/sections/other/constraints.qmd
mmm trying to do grads with respect to implausibility but not clear how to plot

    # # Gradient field:
    # u = []
    # v = []
    # for (x, y) in inputs
    #     g = -loss_grads(generator, M, ce, [x, y][:,:])
    #     push!(u, η * g[1])
    #     push!(v, η * g[2])
    # end
    # Plots.quiver!(x1, x2, quiver=(u, v))

    # Counterfactuals:
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        Plots.scatter!(x[1,:], x[2,:], label=["CE (y⁺=1)" "CE (y⁺=2)"], ms=15, shape=:star, color=yhat, group=yhat)
    end
    display(plt)

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

>>>>

    # Gradient field:
    targets = Flux.onehotbatch(fill(2,size(x,2)), [1,2])
    samples = ce_data.X[:,ce_data.output_encoder.labels.==2][:,rand(1:end,size(x,2))]
    u = []
    v = []
    η = 0.1
    for (i,ce) in enumerate(eachcol(x))
        grads = Flux.gradient((m,x,s,t) -> implausibility(m,x,s,t)[1], model, ce, samples[:,i], targets[:,i])
        g = grads[1].layers[1].weight
        push!(u, η * g[1])
        push!(v, η * g[2])
    end
    Plots.quiver!(x1, x2, quiver=(u, v))

    # Counterfactuals:
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        if any(yhat.==2)
            Plots.scatter!(x[1,yhat.==2], x[2,yhat.==2], label=["CE (y⁺=1)" "CE (y⁺=2)"], ms=15, shape=:star, color=yhat[yhat.==2], group=yhat[yhat.==2])
        end
    end
    display(plt)

@@

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 5,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )
